---
title: "Vancouver Tree Inventory"
author: "Stefanie Lumnitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
params:
    fileName:
        value: x
---

```{r, echo=FALSE}
# load libraries
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
suppressWarnings(suppressPackageStartupMessages(library(dplyr)))
suppressWarnings(suppressPackageStartupMessages(library(DT)))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(leaflet))
library(knitr)
library(markdown)
library(rmarkdown)
```

```{r load-genus, include=FALSE}
# define Variables and file names
newBaseName <-paste(gsub(".png", basename(fileName), replacement = "")) # e.g. "StreetTrees_WestPointGrey"
newFileName <- paste(gsub(".png", gsub("StreetTrees_", # e.g. "WestPointGrey
																			 x= basename(fileName),
																			 replacement = ""),
													replacement = ""))
tree_data <- paste0("../../data/", newBaseName, ".csv") # path to csv
area_data <- paste0("../../data/", newBaseName, ".tsv") # path to .tsv
current_png <- paste0("../../images/", newBaseName, ".png") # path to png

genus_data <- read.delim(area_data, header = TRUE) # load .tsv
trees <- read.csv(tree_data, stringsAsFactors = FALSE) %>% # load .csv
	select(lon="LONGITUDE",
		   lat="LATITUDE",
		   std_street="STD_STREET",
		   on_street="ON_STREET",
		   neighbourhood="NEIGHBOURHOOD_NAME",
		   height="HEIGHT_RANGE_ID",
		   diameter="DIAMETER",
		   date_planted="DATE_PLANTED",
		   genus="GENUS_NAME",
		   species="SPECIES_NAME",
		   common_name="COMMON_NAME") %>% 
	filter(!(lat==0)) %>% 
	transform(date_planted = as.Date(as.character(date_planted), "%Y%m%d"))
```


Data in this report can be accessed through the [Vancouver Street Trees](https://vancouvertrees.shinyapps.io/vancouver_street_trees/) inventory.

<br><br>

## Tree genus report for `r newBaseName`

### Most common genus

The most common genus in `r newFileName` is `r with(genus_data, genus[which.max(number)])` with `r max(genus_data$number)` observaitions.

<br><br>

```{r, echo=FALSE, fig.height=8}
include_graphics(current_png)
```

<br><br>

### Tree species overview

What tree species at the genus level can be found in `r newBaseName`:

```{r, echo=FALSE}
datatable(trees)
```

<br><br>

And where are the trees:

```{r}
trees %>% 
	leaflet() %>% addTiles() %>%
    		fitBounds(~min(lon), ~min(lat), ~max(lon), ~max(lat)) %>% 
    		addCircles(lng = ~lon, lat = ~lat, label=~as.character(genus))
```

